sdmTMB: an R package for fast, flexible, and user-friendly generalized linear mixed effects models with spatial and spatiotemporal random fields

### 2022-11-02 doc/paper-jss/model-description.Rmd
Fixes

We include tables of all major indices (Table \@ref(tab:indices)) and symbols (Table \@ref(tab:symbols)).

\begin{table}[!h]
\caption{Subscript notation}
\centering
\begin{tabular}[t]{ll}
\toprule
Symbol & Description\\
\midrule
$\s$ & Index for space; a vector of x and y coordinates\\
$t$ & Index for time\\
$g$ & Group\\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\caption{Symbol notation, code representation (in model output or in model template code), and descriptions.}
\centering
\begin{tabular}[t]{lll}
\toprule
Symbol & Code & Description\\
\midrule
$y$ & \texttt{y\_i} & Observed response data\\
$\mu$ & \texttt{mu\_i} & Mean\\
$\phi$ & \texttt{phi} & A dispersion parameter for a distribution\\
$f$ & \texttt{fit\$family\$link} & Link function\\
$f^{-1}$ & \texttt{fit\$family\$linkinv} & Inverse link function\\
$\boldsymbol{\beta}$ & \texttt{b\_j} & Parameter vector\\
$\boldsymbol{X}$ & \texttt{X\_ij} & A predictor model matrix\\
$O_{\s, t}$ & \texttt{offset} & An offset variable at point $\s$ and time $t$\\
\addlinespace
$\omega_{\s}$ & \texttt{omega\_s} & Spatial random field at point $\s$ (knot)\\
$\omega_{\s}^*$ & \texttt{omega\_s\_A} & Spatial random field at point $\s$ (interpolated)\\
$\zeta_{\s}$ & \texttt{zeta\_s} & Spatially varying coefficient random field at point $\s$ (knot)\\
$\zeta_{\s}^*$ & \texttt{zeta\_s\_A} & Spatially varying coefficient random field at point $\s$ (interpolated)\\
$\epsilon_{\s, t}$ & \texttt{epsilon\_st} & Spatiotemporal random field at point $\s$ and time $t$ (knot)\\
$\epsilon_{\s, t}^*$ & \texttt{epsilon\_st\_A} & Spatiotemporal random field at point $\s$ and time $t$ (interpolated)\\
$\delta_{\s,t}$ & \texttt{b\_t} & AR(1) or random walk spatiotemporal deviations (knot)\\
$\alpha_g$ & \texttt{RE} & IID random intercept deviation for group $g$\\
\addlinespace
$\boldsymbol{\Sigma}_\omega$ & \texttt{-} & Spatial random field covariance matrix\\
$\boldsymbol{\Sigma}_\zeta$ & \texttt{-} & Spatially varying coefficient random field covariance matrix\\
$\boldsymbol{\Sigma}_\epsilon$ & \texttt{-} & Spatiotemporal random field covariance matrix\\
$\boldsymbol{Q}_\omega$ & \texttt{Q\_s} & Spatial random field precision matrix\\
$\boldsymbol{Q}_\zeta$ & \texttt{Q\_s} & Spatially varying coefficient random field precision matrix\\
$\boldsymbol{Q}_\epsilon$ & \texttt{Q\_st} & Spatiotemporal random field precision matrix\\
\addlinespace
$\sigma_\alpha^2$ & \texttt{sigma\_G} & IID random intercept variance\\
$\sigma_\epsilon^2$ & \texttt{sigma\_E} & Spatiotemporal random field marginal variance\\
$\sigma_\omega^2$ & \texttt{sigma\_O} & Spatial random field marginal variance\\
$\sigma_\zeta^2$ & \texttt{sigma\_Z} & Spatially varying coefficient random field marginal variance\\
$\kappa_\omega$ & \texttt{kappa(0)} & Spatial decorrelation rate\\
$\kappa_\epsilon$ & \texttt{kappa(1)} & Spatiotemporal decorrelation rate\\
\addlinespace
$\rho$ & \texttt{ar1\_rho} & Correlation between random fields in subsequent time steps\\
$\boldsymbol{A}$ & \texttt{A} & Sparse projection matrix to interpolate between knot and data locations\\
$\boldsymbol{H}$ & \texttt{H} & 2-parameter rotation matrix used to define anisotropy\\
\bottomrule
\end{tabular}
\end{table}

>>>>

We include tables of all major indices (Table \ref{tab:indices}) and symbols (Table \ref{tab:symbols}).

\begin{table}[!h]
\caption{Subscript notation}
\centering
\begin{tabular}[t]{ll}
\toprule
Symbol & Description\\
\midrule
$\s$ & Index for space; a vector of x and y coordinates\\
$t$ & Index for time\\
$g$ & Group\\
\bottomrule
\label{tab:indices}
\end{tabular}
\end{table}

\begin{table}
\caption{Symbol notation, code representation (in model output or in model template code), and descriptions.}
\centering
\begin{tabular}[t]{lll}
\toprule
Symbol & Code & Description\\
\midrule
$y$ & \texttt{y\_i} & Observed response data\\
$\mu$ & \texttt{mu\_i} & Mean\\
$\phi$ & \texttt{phi} & A dispersion parameter for a distribution\\
$f$ & \texttt{fit\$family\$link} & Link function\\
$f^{-1}$ & \texttt{fit\$family\$linkinv} & Inverse link function\\
$\boldsymbol{\beta}$ & \texttt{b\_j} & Parameter vector\\
$\boldsymbol{X}$ & \texttt{X\_ij} & A predictor model matrix\\
$O_{\s, t}$ & \texttt{offset} & An offset variable at point $\s$ and time $t$\\
\addlinespace
$\omega_{\s}$ & \texttt{omega\_s} & Spatial random field at point $\s$ (knot)\\
$\omega_{\s}^*$ & \texttt{omega\_s\_A} & Spatial random field at point $\s$ (interpolated)\\
$\zeta_{\s}$ & \texttt{zeta\_s} & Spatially varying coefficient (SVC) random field at point $\s$ (knot)\\
$\zeta_{\s}^*$ & \texttt{zeta\_s\_A} & SVC random field at point $\s$ (interpolated)\\
$\epsilon_{\s, t}$ & \texttt{epsilon\_st} & Spatiotemporal random field at point $\s$ and time $t$ (knot)\\
$\epsilon_{\s, t}^*$ & \texttt{epsilon\_st\_A} & Spatiotemporal random field at point $\s$ and time $t$ (interpolated)\\
$\delta_{\s,t}$ & \texttt{b\_t} & AR(1) or random walk spatiotemporal deviations (knot)\\
$\alpha_g$ & \texttt{RE} & IID random intercept deviation for group $g$\\
\addlinespace
$\boldsymbol{\Sigma}_\omega$ & \texttt{-} & Spatial random field covariance matrix\\
$\boldsymbol{\Sigma}_\zeta$ & \texttt{-} & Spatially varying coefficient random field covariance matrix\\
$\boldsymbol{\Sigma}_\epsilon$ & \texttt{-} & Spatiotemporal random field covariance matrix\\
$\boldsymbol{Q}_\omega$ & \texttt{Q\_s} & Spatial random field precision matrix\\
$\boldsymbol{Q}_\zeta$ & \texttt{Q\_s} & Spatially varying coefficient random field precision matrix\\
$\boldsymbol{Q}_\epsilon$ & \texttt{Q\_st} & Spatiotemporal random field precision matrix\\
\addlinespace
$\sigma_\alpha^2$ & \texttt{sigma\_G} & IID random intercept variance\\
$\sigma_\epsilon^2$ & \texttt{sigma\_E} & Spatiotemporal random field marginal variance\\
$\sigma_\omega^2$ & \texttt{sigma\_O} & Spatial random field marginal variance\\
$\sigma_\zeta^2$ & \texttt{sigma\_Z} & Spatially varying coefficient random field marginal variance\\
$\kappa_\omega$ & \texttt{kappa(0)} & Spatial decorrelation rate\\
$\kappa_\epsilon$ & \texttt{kappa(1)} & Spatiotemporal decorrelation rate\\
\addlinespace
$\rho$ & \texttt{ar1\_rho} & Correlation between random fields in subsequent time steps\\
$\boldsymbol{A}$ & \texttt{A} & Sparse projection matrix (from knot to data locations)\\
$\boldsymbol{H}$ & \texttt{H} & 2-parameter rotation matrix used to define anisotropy\\
\bottomrule
\label{tab:symbols}
\end{tabular}
\end{table}
